{\bf Landslide: A New Race-Finding Tool for 15-410}

### 2017-02-28 landslide-lecture/2017/lecture.tex
update lecture for s17
minor lecture fix

\institute[CMU 15-410]{Carnegie Mellon University - 15-410}
\date[]{2016, September 28}

@@

	Okay, wait a sec...
	\begin{itemize}
		\item How can you possibly execute {\em every possible} interleaving?
		%\item How can you know where preempting matters most?
		\item How did you know to draw that tree's branches where they matter?
	\end{itemize}
\end{frame}

@@

	Systematic tests are {\em parameterized} by the set of PPs.
	\begin{itemize}
		\item $n$ PPs and $k$ threads $\Rightarrow$ state space size is $n^k$.
		\item Need to choose PPs very carefully for test to be effective.
		\begin{itemize}
			\item ``Effective'' = both comprehensive and feasible.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{About The Project}
	\textbf{About me}: 6th year graduate student, advised by Garth Gibson
	\begin{itemize}
		\item TAed 15-410 for 3 semesters during undergrad
		%\item 1st graduate year was 5th year M.S., rest in Ph.D. program
		\item Landslide's publication history
		\begin{itemize}
			\item Master's thesis
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/thesis.pdf}
			\end{itemize}
			\item Conference paper (to appear in OOPSLA this november)
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/oopsla.pdf}
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Iterative Deepening of Preemption Points}
	Goal: Run the best tests for a given CPU budget.
	%\begin{itemize}
	%	\item Technique: ``Iterative Deepening''
	%\end{itemize}
	%\linegap

@@

	To participate\dots
	\begin{itemize}
		%\item Review this lecture and study information sheet
		\item Meet prerequisites of passing P2 tests
		\item Complete sign-up form online to get further instructions
			\begin{itemize}
				\item \url{http://tinyurl.com/landslide-p2-f16}
			\end{itemize}
		\item Optional ``Landslide clinic'' for in-person tech (or moral) support
			\begin{itemize}
				\item Mid-next-week, room and time TBD
			\end{itemize}
		\item Use Landslide in addition to stress tests until P2 is due!
	\end{itemize}
	\linegap

>>>>

\institute[CMU 15-410]{Carnegie Mellon University - 15-410}
\date[]{2017, February 20}

@@

	Okay, wait a sec...
	\pause
	\begin{itemize}
		\item How can you possibly execute {\em every possible} interleaving?
		%\item How can you know where preempting matters most?
		\item How did you know to draw that tree's branches where they matter?
	\end{itemize}
\end{frame}

@@

	Systematic tests are {\em parameterized} by the set of PPs.
	\begin{itemize}
		\item $n$ PPs and $k$ threads $\Rightarrow$ state space size is $O(n^k)$.
		\item Need to choose PPs very carefully for test to be effective.
		\begin{itemize}
			\item ``Effective'' = both comprehensive and feasible.
		\end{itemize}
	\end{itemize}
\end{frame}

@@

\begin{frame}{About The Project}
	\textbf{About me}: 6th year graduate student, advised by Garth Gibson
	\begin{itemize}
		\item TAed 15-410 for 3 semesters during undergrad
		%\item 1st graduate year was 5th year M.S., rest in Ph.D. program
		\item Landslide's publication history
		\begin{itemize}
			\item Master's thesis
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/thesis.pdf}
			\end{itemize}
			\item Conference paper (OOPSLA 2016)
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/oopsla.pdf}
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Iterative Deepening of Preemption Points}
	Goal: Run the best tests for a given CPU budget.
	%\begin{itemize}
	%	\item Technique: ``Iterative Deepening''
	%\end{itemize}
	\linegap

@@

	To participate\dots
	\begin{itemize}
		%\item Review this lecture and study information sheet
		\item Meet prerequisites of passing P2 tests
		\item Complete sign-up form online to get further instructions
			\begin{itemize}
				\item \url{http://tinyurl.com/landslide-p2-s17}
			\end{itemize}
		\item Optional ``Landslide clinic'' for in-person tech (or moral) support
			\begin{itemize}
				\item Later this week, room and time TBD
			\end{itemize}
		%\item Use Landslide in addition to stress tests until P2 is due!
	\end{itemize}
	\linegap
